---
title: "Chp8"
author: "OUYANG YUCHEN"
date: "2023-04-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Chp8 Data Import

### 8.2.4 Exercise

1.  What function would you use to read a file where fields were separated with "\|"?

    <div>

    read_delim(delim="\|")

    </div>

2.  Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?

    <div>

    Check [`?read_delim()`]{style="color:red"}, `col_names`, `col_types`, `id`, `col_select`, `lazy`, `progress`...

    </div>

3.  What are the most important arguments to read_fwf()?

    <div>

    The most important arg is `col_positions`, which tells the function where data columns begin\
    and end.

    </div>

4.  Sometimes strings in a CSV file contain commas. To prevent them from causing problems, they need to be surrounded by a quoting character, like " or '. By default, read_csv() assumes that the quoting character will be ". To read the following text into a data frame, what argument to read_csv() do you need to specify?

    ```{r 824-4}
    library(tidyverse)
    read_csv("x,y\n1,'a,b'",quote="'")
    ```

5.  Identify what is wrong with each of the following inline CSV files. What happens when you run the code?

    ```{r 824-5-1}
    # fewer col_names, should be columns
    read_csv("a,b\n1,2,3\n4,5,6")
    ```
    
    ```{r 824-5-2}
    # the number of columns and data mismateched
    read_csv("a,b,c\n1,2\n1,2,3,4")
    ```
    
    ```{r 824-5-3}
    # quote inconstency
    read_csv("a,b\n\"1")
    ```
    
    ```{r 824-5-4}
    # mixed numbers and characters
    read_csv("a,b\n1,2\na,b")
    ```
    
    ```{r 824-5-5}
    #non-csv delimiter ";"
    read_csv("a;b\n1;3")
    ```

6.  Practice referring to non-syntactic names in the following data frame by:
    ```{r 824-6}
    annoying <- tibble(
    `1` = 1:10,
    `2` = `1` * 2 + rnorm(length(`1`))
    )
    ```

    a.  Extracting the variable called `1`.
    
    ```{r 824-6a}
    annoying$`1`
    ```

    b.  Plotting a scatter plot of `1` vs.`2`.
    ```{r 824-6b}
    ggplot(annoying,aes(x=`1`,y=`2`))+geom_point()
    ```

    c.  Creating a new column called `3`, which is `2` divided by `1`.
    ```{r 824-6c}
    annoying <- annoying %>% mutate(`3` = `2`/`1`)
    ```

    d.  Renaming the columns to `one`, `two`, and `three`.
    ```{r 824-6d}
    annoying <- annoying %>% rename(
      "one" = `1`,
      "two" = `2`,
      "three" = `3`)
    ```

