---
title: "Chp2_Data_Visualization"
author: "OUYANG YUCHEN"
date: "2023-04-23"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Visualization

### Load library

Before we do the exercise, we need to install and load relevant library.

```{r load library}
library(tidyverse)
library(palmerpenguins)
```

### Table info

```{r table info}
glimpse(penguins)
```

### 2.2.5 Exercises

1.  How many rows are in `penguins`? How many columns?

```{r rows/columns}
data("penguins")
nrow(penguins) 
ncol(penguins)
```

2.  What does the `bill_depth_mm` variable in the `penguins` data frame describe? Read the help for `?penguins` to find out.

```{r bill_depth_mm}
# bill_depth_mm : a number denoting bill depth (millimeters)
?penguins
```

3.  Make a scatterplot of `bill_depth_mm` vs. `bill_length_mm`. That is, make a scatterplot with `bill_depth_mm` on the y-axis and `bill_length_mm` on the x-axis. Describe the relationship between these two variables.

```{r plot bill d/l}
ggplot(data = penguins,
       mapping = aes(x=bill_length_mm, y=bill_depth_mm, color = species)
) + geom_point() + geom_smooth(method = 'lm')  + labs(
        title = "Bill length vs. Bill depth (by shape)",
        x = "Bill length / mm ", y = "Bill depth / mm",
        color = "Species"
)
```

4.  What happens if you make a scatterplot of `species` vs. `bill_depth_mm`? What might be a better choice of geom?

```{r plot}
# better use box plot
ggplot(data = penguins,
       mapping = aes(x=species, y=bill_depth_mm, color=species)
) + geom_boxplot() 
```

5.  Why does the following give an error and how would you fix it?

```{r e5}
# error: missing aesthetics: x and y
ggplot(data = penguins,
       mapping = aes(x="",y="")
       ) + geom_point()
```

6.  What does the `na.rm` argument do in `geom_point()`? What is the default value of the argument? Create a scatterplot where you successfully use this argument set to `TRUE`.

```{r e6}
?geom_point
# na.rm: 	If FALSE, the default, missing values are removed with a warning. If TRUE, missing values are silently removed
ggplot(data = penguins,
       mapping = aes(x=bill_length_mm, y=bill_depth_mm, color = species)
) + geom_point(na.rm = TRUE) + geom_smooth(method = 'lm', na.rm = TRUE)  + labs(
        title = "Bill length vs. Bill depth (by shape)",
        x = "Bill length / mm ", y = "Bill depth / mm",
        color = "Species"
)
```

7.  Add the following caption to the plot you made in the previous exercise: "Data come from the `palmerpenguins` package." Hint: Take a look at the documentation for `labs()`.

```{r e7}
ggplot(data = penguins,
       mapping = aes(x=bill_length_mm, y=bill_depth_mm, color = species)
) + geom_point(na.rm = TRUE) + geom_smooth(method = 'lm', na.rm = TRUE)  + labs(
        title = "Data come from the palmerpenguins package",
        x = "Bill length / mm ", y = "Bill depth / mm",
        color = "Species"
)
```

8.  Recreate the following visualization. What aesthetic should `bill_depth_mm` be mapped to? And should it be mapped at the global level or at the geom level?

```{r e8}
ggplot(data = penguins,
       mapping = aes(x=flipper_length_mm, y=body_mass_g, color = bill_depth_mm)
) + geom_point(na.rm = TRUE) + geom_smooth(method = 'loess', na.rm = TRUE)   + scale_color_gradient(low = "darkblue")
```

9.  Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

```{r e9}
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g, color = island)
) +
  geom_point() +
  geom_smooth(se = FALSE)
```

#### 10.Will these two graphs look different? Why/why not?

```{r e10-1}
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g)
) +
  geom_point() +
  geom_smooth()
```

```{r e10-2}
ggplot() +
  geom_point(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  ) +
  geom_smooth(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  )
```

### 2.4.3. Exercises

1.  Make a bar plot of species of penguins, where you assign species to the y aesthetic. How is this plot different?

```{r 2-4-3-e1}
ggplot(data = penguins, aes(y = species)) + geom_bar()
```

2.  How are the following two plots different? Which aesthetic, color or fill, is more useful for changing the color of bars?

```{r 2-4-3-e2}
ggplot(penguins, aes(x = species)) +
  geom_bar(color = "red")

# more useful changing color
ggplot(penguins, aes(x = species)) +
  geom_bar(fill = "red")
```

3.  What does the bins argument in geom_histogram() do?

controls the number of bins along the X-axis.

4.  Make a histogram of the `carat` variable in the `diamonds` dataset that is available when you load the tidyverse package. Experiment with different `binwidths`. What `binwidth` reveals the most interesting patterns?

```{r 2-4-3-e4}
ggplot(data = diamonds, aes(x = carat)) + geom_histogram(binwidth = 0.3)
```

### 2.5.5 Exercise

1.  The`mpg` data frame that is bundled with the ggplot2 package contains 234 observations collected by the US Environmental Protection Agency on 38 car models. Which variables in `mpg` are categorical? Which variables are numerical? (Hint: Type `?mpg` to read the documentation for the dataset.) How can you see this information when you run `mpg`?

```{r 2-5-5-e1}
?mpg
mpg
print("categorical: manufacturer, model, trans, drv, fl, class")
print("numerical: displ, year, cyl, cty, hwy")
```

2.  Make a scatterplot of `hwy` vs. `displ` using the `mpg` data frame. Next, map a third, numerical variable to `color`, then `size`, then both `color` and `size`, then `shape`. How do these aesthetics behave differently for categorical vs. numerical variables?

```{r 2-5-5-e2-1}
ggplot(mpg, aes(x=hwy,y=displ, color=cty)) + geom_point()
```

```{r 2-5-5-e2-2}
ggplot(mpg, aes(x=hwy,y=displ, size=cty)) + geom_point()
```

```{r 2-5-5-e2-3}
ggplot(mpg, aes(x=hwy,y=displ, color=cty, size=cty)) + geom_point()
```

```{r 2-5-5-e2-4}
# ggplot(mpg, aes(x=hwy,y=displ,shape=cty) + geom_point()
# Error: A continuous variable cannot be mapped to the shape aesthetic       
```

3.  In the scatterplot of `hwy` vs. `displ`, what happens if you map a third variable to `linewidth`?

```{r 2-5-5-e3}
ggplot(mpg, aes(x=hwy,y=displ,linewidth=0.5)) + geom_point()
```

In the scatterplot, linewidth does nothing, as there is no line

4.  What happens if you map the same variable to multiple aesthetics?

```{r 2-5-5-e4}
ggplot(mpg, aes(x=hwy,y=displ, color = hwy, size = displ)) + geom_point()
```

In the above plot, `hwy` is mapped to both location on the y-axis and color, and `displ` is mapped to both location on the x-axis and size. The code works and produces a plot, even if it is a bad one. Mapping a single variable to multiple aesthetics is redundant. Because it is redundant information, in most cases avoid mapping a single variable to multiple aesthetics.

5.  Make a scatterplot of `bill_depth_mm` vs. `bill_length_mm` and color the points by `species`. What does adding coloring by `species` reveal about the relationship between these two variables? What about faceting by `species`?

```{r 2-5-5-e5-1}
ggplot(penguins,aes(x=bill_length_mm,y=bill_depth_mm,color=species)) + geom_point()
```

```{r 2-5-5-e5-2}
ggplot(penguins,aes(x=bill_length_mm,y=bill_depth_mm)) + geom_point()+facet_wrap(~species)
```

6.  Why does the following yield two separate legends? How would you fix it to combine the two legends?

```{r 2-5-5-e6}
#Use same labels for both color and shape
ggplot(penguins) + geom_point(aes(x = bill_length_mm, y = bill_depth_mm, color = species, shape = species)) + labs(color = "Species",shape="Species")
```

7.  Create the two following stacked bar plots. Which question can you answer with the first one? Which question can you answer with the second one?

```{r 2-5-5-e7-1}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(position = "fill")
```

This plot demonstrates the portion of different species in a island

```{r 2-5-5-e7-2}
ggplot(penguins, aes(x = species, fill = island)) +
  geom_bar(position = "fill")
```

This plot shows the distribution of the species in different islands.

### 2.6.1 Exercise

1.  Run the following lines of code. Which of the two plots is saved as `mpg-plot.png`? Why?

```{r 2-6-1-e1}
ggplot(mpg, aes(x = class)) +
  geom_bar()
ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_point()
ggsave("mpg-plot.png") 
```

bar plot and scatter plot.

2.  What do you need to change in the code above to save the plot as a PDF instead of a PNG? How could you find out what types of image files would work in `ggsave()`?

```{r 2-6-1-e2, warning=FALSE}
ggplot(mpg, aes(x = class)) +
  geom_bar()
ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_point()
ggsave("mpg-plot.pdf") 
```

You can use `?ggsave` to figure out the information.
