---
title: "Chp2_Data_Visualization"
author: "OUYANG YUCHEN"
date: "2023-04-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Visualization
### Load library

Before we do the exercise, we need to install and load relevant library.
```{r load library}
library(tidyverse)
library(palmerpenguins)
library(ggthemes)
```

### Table info
```{r table info}
glimpse(penguins)
```

### 2.2.5 Exercises
1. How many rows are in `penguins`? How many columns?

```{r rows/columns}
data("penguins")
nrow(penguins) 
ncol(penguins)
```

2. What does the `bill_depth_mm` variable in the `penguins` data frame describe? Read the help for `?penguins` to find out.

```{r bill_depth_mm}
# bill_depth_mm : a number denoting bill depth (millimeters)
?penguins
```

3. Make a scatterplot of `bill_depth_mm` vs. `bill_length_mm`. That is, make a scatterplot with `bill_depth_mm` on the y-axis and `bill_length_mm` on the x-axis. Describe the relationship between these two variables.

```{r plot bill d/l}
ggplot(data = penguins,
       mapping = aes(x=bill_length_mm, y=bill_depth_mm, color = species)
) + geom_point() + geom_smooth(method = 'lm')  + labs(
        title = "Bill length vs. Bill depth (by shape)",
        x = "Bill length / mm ", y = "Bill depth / mm",
        color = "Species"
)
```
4. What happens if you make a scatterplot of `species` vs. `bill_depth_mm`? What might be a better choice of geom?

```{r plot}
# better use box plot
ggplot(data = penguins,
       mapping = aes(x=species, y=bill_depth_mm, color=species)
) + geom_boxplot() 
```

5. Why does the following give an error and how would you fix it?

```{r e5}
# error: missing aesthetics: x and y
ggplot(data = penguins,
       mapping = aes(x="",y="")
       ) + geom_point()
```

6. What does the `na.rm` argument do in `geom_point()`? What is the default value of the argument? Create a scatterplot where you successfully use this argument set to `TRUE`.

```{r e6}
?geom_point
# na.rm: 	If FALSE, the default, missing values are removed with a warning. If TRUE, missing values are silently removed
ggplot(data = penguins,
       mapping = aes(x=bill_length_mm, y=bill_depth_mm, color = species)
) + geom_point(na.rm = TRUE) + geom_smooth(method = 'lm', na.rm = TRUE)  + labs(
        title = "Bill length vs. Bill depth (by shape)",
        x = "Bill length / mm ", y = "Bill depth / mm",
        color = "Species"
)
```

7. Add the following caption to the plot you made in the previous exercise: “Data come from the `palmerpenguins` package.” Hint: Take a look at the documentation for `labs()`.

```{r e7}
ggplot(data = penguins,
       mapping = aes(x=bill_length_mm, y=bill_depth_mm, color = species)
) + geom_point(na.rm = TRUE) + geom_smooth(method = 'lm', na.rm = TRUE)  + labs(
        title = "Data come from the palmerpenguins package",
        x = "Bill length / mm ", y = "Bill depth / mm",
        color = "Species"
)
```

8. Recreate the following visualization. What aesthetic should `bill_depth_mm` be mapped to? And should it be mapped at the global level or at the geom level?

```{r e8}
ggplot(data = penguins,
       mapping = aes(x=flipper_length_mm, y=body_mass_g, color = bill_depth_mm)
) + geom_point(na.rm = TRUE) + geom_smooth(method = 'loess', na.rm = TRUE)   + scale_color_gradient(low = "darkblue")
```

9. Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

```{r e9}
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g, color = island)
) +
  geom_point() +
  geom_smooth(se = FALSE)
```

#### 10.Will these two graphs look different? Why/why not?

```{r e10-1}
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g)
) +
  geom_point() +
  geom_smooth()
```

```{r e10-2}
ggplot() +
  geom_point(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  ) +
  geom_smooth(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  )
```