---
title: "Chp6"
author: "OUYANG YUCHEN"
date: "2023-04-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Chp6 data tidying

```{r prequisite}
library(tidyverse)
```

### 6.2.1 Exercise

1.  For each of the sample tables, describe what each observation and each column represents.

2.  Sketch out the process you'd use to calculate the `rate` for `table2` and `table3`. You will need to perform four operations:

    a.  Extract the number of TB cases per country per year.

    ```{r e2a}
    cases_t2 <- filter(table2,type=="cases") %>% rename(cases = count) %>% arrange(country,year)
    ```

    b.  Extract the matching population per country per year.

    ```{r e2b}
    population_t2 <- filter(table2,type=="population") %>% rename(population = count) %>%    arrange(country,year)
    ```

    c.  Divide cases by population, and multiply by 10000.

    ```{r e2c}
    case_n_population <- tibble(
      country = cases_t2$country,
      year = cases_t2$year,
      popluation=population_t2$population,
      cases=cases_t2$cases
    ) %>% 
      mutate(cdp = (cases_t2$cases/population_t2$population)*1000)
    ```

    d.  Store back in the appropriate place.

    ```{r e2d}
    case_n_population <- case_n_population %>% mutate(type = "cases_per_pop") %>% rename(count = cdp) %>% select(country,year,type,count)
    bind_rows(table2,case_n_population) %>% arrange(country,year,type,count)
    ```
